---
---
title: "Bass Model"
author: "Anna Aghaloyan"
date: "10/18/2024"
output: md_document
---

---

```{r}
# Load the rmarkdown package
library(rmarkdown)

# Render the R Markdown file, and specify the output file name after rendering
rmarkdown::render(input = "Bass Model Anna Aghaloyan.Rmd", 
                  output_format = "md_document")

# Rename the output file to your desired name
file.rename("Bass_Model_Anna_Aghaloyan.md", "md_document.md")

```

This paper focuses on the KIA EV6, one of TIME's best inventions of 2023. It will explore the vehicle's predecessor in innovation, apply the Bass Diffusion Model to estimate its adoption, and forecast the number of global users.

Although electric vehicles are generally expensive, KIA’s EV6 GT—named the 2023 World Performance Car at the World Car Awards—stands out as an affordable alternative, costing nearly half of what other EVs do without compromising on performance. The EV6 GT accelerates from 0 to 100 km/h in just 3.4 seconds, reaches a top speed of 260 kph, and even includes a "drift mode" (TIME, 2023).

Kia's EV6 GT encapsulates the brand's philosophy, which centers around the idea that movement drives human progress. It seeks to empower people to explore new destinations, form meaningful connections, and embrace fresh experiences. Kia aims to inspire its customers by offering innovative products, immersive vehicle interiors, and services that free up time for personal pursuits (TIME, 2023).

A comparable past innovation is Tesla’s electric vehicle series. Both the KIA EV6 GT and Tesla models represent a strong commitment to electric mobility, offering environmentally friendly alternatives to gasoline-powered vehicles. These brands focus on sustainability, integrating advanced technology to enhance performance, efficiency, and the overall driving experience. They also share sleek, futuristic designs that reflect a modern approach to vehicle aesthetics. Moreover, both the KIA EV6 GT and Tesla aim to deliver a premium driving experience, offering responsive handling, cutting-edge safety features, and luxurious interiors. Together, they play a crucial role in the ongoing shift toward more sustainable transportation solutions.

For the analysis of look-alike innovation, sales data from 2014 to 2023, obtained from Statista, will be used for comparison and Bass Model diffusion estimations.

\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(ggpubr)
library(knitr)
library(diffusion)
library(readxl)
library(DIMORA)
```


```{r message=FALSE, warning=FALSE, echo=FALSE}
tesla <- read_excel("Tesla Sales.xlsx")

```


```{r echo=FALSE}

tesla$Year <- as.numeric(tesla$Year)

ggplot(data = tesla, aes(x = Year, y = `Tesla sales in 1000 units`)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label = `Tesla sales in 1000 units`), 
            position = position_dodge(width = 0.5), vjust = -0.5) +
  scale_x_continuous(breaks = seq(2016, 2023, by = 1)) +  
  theme_minimal() +
  labs(title = "Tesla Electric Series World-Wide Sales", x = "", y = "Tesla sales In 1000 Units") +
  theme(plot.title = element_text(hjust = 0.5), axis.text.y = element_blank())

```
The graph illustrates Tesla's global electric vehicle sales from 2016 to 2023, measured in thousands of units. The trend shows a consistent and significant increase in sales year-over-year, with a particularly sharp rise starting in 2021. In 2016, Tesla sold approximately 76,000 units, and by 2023, this number had surged to over 1.8 million units, showcasing Tesla's growing dominance in the electric vehicle market. The steep acceleration in sales from 2021 onwards reflects both the increasing consumer demand for electric vehicles and Tesla's expanding production capacity.


\newpage


```{r echo=FALSE}
# Summarize the sales data for Tesla
summary(BM(tesla$`Tesla sales in 1000 units`))
```
ased on the summary of the model, the estimated values for the parameters are as follows: the innovation rate p is approximately  0.003115, the imitation rate, q is approximately  0.534121, and the market potential m is approximately 18067.35. These estimates indicate a relatively low innovation rate and a higher imitation rate, suggesting that while initial adoption may be slow, subsequent uptake through imitation is likely to be significant. The market potential reflects a substantial opportunity for growth in sales, reinforcing the potential for widespread acceptance of the innovation.


\newpage

```{r echo=FALSE, message=FALSE, warning=FALSE}
tesla <- read_excel("Tesla Sales.xlsx")
tesla$Year <- as.numeric(tesla$Year)
tesla$`Tesla sales in 1000 units` <- as.numeric(tesla$`Tesla sales in 1000 units`)

tesla_data <- data.frame(Year = tesla$Year, Sales = tesla$`Tesla sales in 1000 units`)

diff_m = diffusion(tesla_data$Sales)
p = round(diff_m$w, 4)[1]
q = round(diff_m$w, 4)[2]
m = round(diff_m$w, 4)[3]
diff_m


```
We have almost the same values as for Method 1. I will choose the parameters from the first method.
```{r}

p <- 0.003115
q <- 0.534121
m <- 18067.35

bass.f <- function(t,p,q){((p+q)^2/p)*exp(-(p+q)*t) / (1+(q/p)*exp(-(p+q)*t))^2}

bass.F <- function(t,p,q){(1-exp(-(p+q)*t)) / (1+(q/p)*exp(-(p+q)*t))}

tesla$pred_sales <- bass.f(1:8, p = p, q = q) * m

ggplot(tesla, aes(x = Year, y = `Tesla sales in 1000 units`)) +
  geom_bar(stat = 'identity', fill = 'steelblue') +
  geom_point(aes(x = Year, y = pred_sales), color = 'red', size = 3) +
  scale_x_continuous(breaks = seq(2016, 2023, by = 1)) +
  labs(title = 'Tesla Electric Series World-Wide Sales and Predicted Sales', 
       x = 'Year', 
       y = 'Sales (in 1000 units)') +
  theme_minimal()

```

\newpage

## Sources\

*The product*

https://time.com/collection/best-inventions-2023/6326978/kia-ev6-gt/

*The look-like product*

https://www.statista.com/statistics/502208/tesla-quarterly-vehicle-deliveries/

